---
title: "Lab 08 - University of Edinburgh Art Collection"
author: "Thomas Huang"
date: "2026-03-04"
output: github_document
---

## Load Packages and Data  

First, let's load the necessary packages:  

```{r load-packages, message = FALSE}
library(tidyverse) 
library(skimr)
```

Now, load the dataset. If your data isn't ready yet, you can leave `eval = FALSE` for now and update it when needed.  


```{r load-data, message = FALSE, eval = FALSE}
# Remove eval = FALSE or set it to TRUE once data is ready to be loaded
uoe_art <- read_csv("data/uoe-art.csv")
```

## Exercise 10

Let's start working with the **title** column by separating the title and the date:  

```{r separate-title-date, error = TRUE}
uoe_art <- uoe_art %>%
  separate(title, into = c("title", "date"), sep = " \\(") %>%
  mutate(year = str_remove(date, "\\)") %>% as.numeric()) %>%
  select(title, artist, year, link) 

save(uoe_art, file = "uoe_art.RData")
```

## Exercise 11  

```{r summarize}
load("/Users/roberthuang/Desktop/Wake/Spring 2026/DSPsych/lab-08-uoe-art/uoe_art.RData")

skim(uoe_art) #108 pieces have artist info missing and 1,574 pieces have year info missing.
```

## Exercise 12

Most pieces are somekind of modern. But one or a few pieces were from around 0AD.
```{r year-hist}
ggplot(uoe_art, aes(x = year)) +
  geom_histogram() +
  geom_histogram(binwidth = 50)
```

## Exercise 13

```{r fix-year-outlier}
outlier <- uoe_art %>%
  filter(!is.na(year)) %>%
  filter(year <= 50) 

outlier #Something was wrong with the piece "Death Mask". This is the link to it: https://collections.ed.ac.uk/art/record/21649?highlight=death+mask. It was actually created in 1964. Something wrong with parsing.

uoe_art <- uoe_art %>%
  mutate(year = if_else(year == 2, 1964, year))

ggplot(uoe_art, aes(x = year)) +
  geom_histogram() +
  geom_histogram(binwidth = 10)
```

## Exercise 14

```{r look-at-artist}
artist_table <- table(uoe_art$artist) %>% 
  as.data.frame() %>% 
  arrange(desc(Freq))

head(artist_table) #Other than the mysterious "Unknown", the most commonly featured artist is Emma Gillies. I don't know Emma. Perhaps Emma went to the university.
```

## Exercise 15

There are 11 pieces with "child" in their title.
```{r child-in-title}
child_in_title <- uoe_art %>% 
  filter(!is.na(title)) %>% 
  filter(str_detect(title, regex("child", ignore_case = TRUE)))

glimpse(child_in_title)
```


